 

### 2021-05-16 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

Tree height also plays a role in buffering where trees upto 20m with higher LAI can maintain lower mean and max temperature and vapor pressure deficit ($VPD$) in the understory. However, beyond a certain tree height, temperature and $VPD$ offset can plateau [@hardwickRelationshipLeafArea2015; @juckerCanopyStructureTopography2018].

### Humidity and evaporative demand
**Humidity also varies across the forest vertical profile, and is generally higher in the understory (Fig. `r fig_NEON_vertical`).**[@mcgregor_tree_nodate]
Along with temperature, dense-canopy forests maintain higher daily maximum relative humidity ($RH$) below-canopy than open-forests and nearby open areas, which is greater in wetter conditions, in warmer than colder months [@vonarxSpatiotemporalEffectsForest2012a]. RH, in combination with temperature, determines $VPD$, an important metric expressing the driving force of water loss from a leaf; tends to be greater in upper-canopy and canopy gaps than in the understory [@fauset_differences_2018; @tymenQuantifyingMicroenvironmentalVariation2017; @niinemetsPhotosyntheticAcclimationSimultaneous2004b].

>>>>

### Humidity and evaporative demand
**Humidity also varies across the forest vertical profile, and is generally higher in the understory (Fig. `r fig_NEON_vertical`).**[@mcgregor_tree_nodate]
Along with temperature, dense-canopy forests maintain higher daily maximum relative humidity ($RH$) below-canopy than open-forests and nearby open areas, which is greater in wetter conditions, in warmer than colder months [@vonarxSpatiotemporalEffectsForest2012a]. RH, in combination with temperature, determines vapor pressure deficit [$VPD$], an important metric expressing the driving force of water loss from a leaf; tends to be greater in upper-canopy and canopy gaps than in the understory [@fauset_differences_2018; @tymenQuantifyingMicroenvironmentalVariation2017; @niinemetsPhotosyntheticAcclimationSimultaneous2004b]. Increased tree height [upto 20m with higher LAI] has also shown to lower mean and max temperature and $VPD$ in the understory. Beyond a certain tree-height, the offset can plateau [@hardwickRelationshipLeafArea2015; @juckerCanopyStructureTopography2018].
